### 2016-09-19 thesis/results/results.tex
tmp commit

@@

>>>>

In this chapter, the relationship between the obesity-associated genetic signatures from previous studies and different cancer types were investigated; new obesity-associated genetic signatures were identified in the data set from \citet{Creighton2012} study; and an attempt was made to find any common genes or pathways across different cancer types.

% TODO: figure out what results go into which section, and present it in a logical order

@@

\section{New obesity-associated genetic signature in \citet{Creighton2012} data set}
\label{sec:creighton_obesity_metagene_new}
